Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-05 ms.tex
added DIRBE vs. 857 GHz linear fit figure

At 1250, 2141 and 3000 GHz, we use the SFD98-reprocessed DIRBE maps. For each
DIRBE band, we determine $s_{i, 857}$ by performing a linear fit to DIRBE as a 
function of \PLANCK~857 GHz, after both have been zodiacal light subtracted and
smoothed to $1^{\circ}$ FWHM, also restricting to the low HI mask of 
$\S$\ref{sec:relzero} (see Figure XX).
% smoothed to 1 degree resolution
% restricted to same low HI mask as in Sect. 3.5.2 analysis
% sentence pointing to figure showing the regressions

>>>>

At 1250, 2141 and 3000 GHz, we use the SFD98-reprocessed DIRBE maps. For each
DIRBE band, we determine $s_{i, 857}$ by performing a linear fit to DIRBE as a 
function of \PLANCK~857 GHz, after both have been zodiacal light subtracted and
smoothed to $1^{\circ}$ FWHM, also restricting to the low HI mask of 
$\S$\ref{sec:relzero} (see Figure \ref{fig:dirbe_slopes}).
% re-mention nside=64 or just bag it?
% restricted to same low HI mask as in Sect. 3.5.2 analysis
% sentence pointing to figure showing the regressions

\begin{figure*}
\begin{center}
\epsfig{file=dirbe_slopes.eps, width=6.5in}
\caption{\label{fig:dirbe_slopes} DIRBE linear fits for correlation slope 
analysis.}
\end{center}
\end{figure*}
